### 2022-01-08 abstract.tex
writing
working
abstract

\begin{abstract}
    \todo[inline]{TODO}
\end{abstract}

>>>>

\begin{abstract}
    \acfp*{NCS} have long been a subject of theoretical study in academia, however, little work has been devoted to repeatable and scalable experimentation.
    With the advent of edge computing and the subsequent proliferation of \acp{NCS} this is quickly becoming a key issue that needs to be addressed.

    In this work, we present a novel, completely software-based approach to this challenge.
    Our core idea rests on a \emph{hardware-in-the-loop} approach in which we emulate a physical plant which communicates over a real network with a controller implemented in software.
    Our approach is furthermore designed and built for the Edge, using a general-purpose programming language and will full compatibility with industry-standard containerization solutions.
\end{abstract}
